\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 poster/main.tex
update plots isze

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  \todo{Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$. But noise here is proportional to $\ell_1$ norm. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$) (v.s. the $\ell_1$ norm in baseline approach).} \todo{grows linear with the dimension.} \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Global sensitivity of $\hellinger$ over $\betad$ distributions takes value at edge ($(0,0)$ point) as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism (v.s. global sensitivity) to improve accuracy.
  {sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.317\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

>>>>

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$. But noise here is proportional to $\ell_1$ norm, which grows linear with the dimension.. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$). %(v.s. the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieve value at edge as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism (v.s. global sensitivity) to improve accuracy.
  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.304\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}
